Extending the Advanced Forensic Format to accommodate Multiple Data Sources, Logical Evidence, Arbitrary Information and Forensic Workflow

### 2009-03-15 paper/paper.tex
bls-small-changes Ignore-this: 77e80e0adaef6db3e24c147848a64636

This paper extends the previous work by adapting AFF to the multiple
heterogeneous data types that might arise in a modern digital
investigation, including data from multiple data storage devices, new
data types (including network packets and memory images), extracted
logical evidence, and forensic workflow. We do this in a manner that
is at once upwards compatible with AFF while adopting the AFF
bit-level specification so that AFF files can be processed using
standard non-forensic tools.  We call the new system AFF4, and use the
phrase AFF1 to refer to the legacy system developed by
Garfinkel.\footnote{Although Garfinkel never changed the AFF bit-level
specification, Garfinkel released AFFLIB implementations with major
version numbers 1, 2 and 3. We therefore call our system AFF4 to avoid
confusion.}

@@

AFF1's flexibility came from the fact that forensic data and metadata
is stored as arbitrary name/value pairs called \emph{segments}. For
example, the first 16MB of a disk image is stored in a segment called
\texttt{page0}, the second 16MB in a segment called \texttt{page1},
\emph{etc.} Because of this flexibility, it was relatively easy for
Garfinkel to extend AFF1 to support encryption, digital signatures, and
the storage of new kinds of metadata such as chain-of-custody
information\cite{garfinkel:affcrypto}.

@@

The AFF4 design adopts a scheme of globally unique identifiers for
identifying and referring to all evidence. We define an AFF4 specific
URN namespace\cite{RFC1737} for our naming scheme (\emph{urn:aff4}).
URNs can then be made unique by use of a unique identifier generated
as per RFC4122\cite{RFC4122}. For example, an AFF4 URN might be
\emph{urn:aff4:bcc02ea5-eeb3-40ce-90cf-7315daf2505e}

In this way we can identify uniquely any evidence without the change
for name collisions. Once a universal identification regime is
created, it is now possible to collect metadata about each object. The
AFF4 model treats metadata as an abstract concept which may exists
independently from the data itself. We term {\em metadata} to be a set
of statements about objects, written in triple notations (Subject,
Attribute, Value), where {\em Subject} is the URN of the object the
statement is made about. Using this system we are able to store
arbitrary attributes about any object in the AFF4 universe.

@@

The AFF4 model is different however. In AFF4 metadata is managed
through a Universal Resolver (perhaps implemented in a database) and
does not really need to exist within a volume. This means that in the
above example, the user will query the resolver about the location of
the volume. The resolver returns a URL to the current location of the
volume. The user's library will then open a HTTP Stream instance to
the location returned and the volume may be opened directly over the
intra-web connection.

>>>>

An important advance of this work is the introduction of storage transformation
functions to the forensic storage container. Prior works simply focused
on forensically sound storage of bitstreams, leaving the necessary activities
of translating low level storage into higher level abstractions at the 
aggregate block (ie. RAID), volume, and filesystem layers in the domain of 
analysis tools, as transiently constructed artifacts. AFF4, through its introduction 
of Map Streams, enables artefacts at all these layers to be stored at zero cost within
the forensic container, which is an important enabler for interoperable 
forensic tools.

This paper extends the previous work by adapting AFF to the multiple
heterogeneous data types that might arise in a modern digital
investigation, including data from multiple data storage devices, new
data types (including network packets and memory images), extracted
logical evidence, and forensic workflow. We do this in a manner that
is at once upwards compatible with AFF while adopting the AFF
bit-level specification so that AFF files can be processed using
standard non-forensic tools. The  We call the new system AFF4, and use the
phrase AFF1 to refer to the legacy system developed by
Garfinkel.\footnote{Although Garfinkel never changed the AFF bit-level
specification, Garfinkel released AFFLIB implementations with major
version numbers 1, 2 and 3. We therefore call our system AFF4 to avoid
confusion.}

@@

AFF1's flexibility came from a data model of forensic data and metadata
stored as arbitrary name/value pairs called \emph{segments}. For
example, the first 16MB of a disk image is stored in a segment called
\texttt{page0}, the second 16MB in a segment called \texttt{page1},
\emph{etc.} Because of this flexibility, it was relatively easy for
Garfinkel to extend AFF1 to support encryption, digital signatures, and
the storage of new kinds of metadata such as chain-of-custody
information\cite{garfinkel:affcrypto}.

@@

The AFF4 design adopts a scheme of globally unique identifiers for
identifying and referring to all evidence. We define an AFF4 specific
URN scheme, which we call the AFF4 URN. URN's of this scheme use the
namespace\cite{RFC1737} \emph{\'aff4\'} and therefore begin with the 
string(\emph{urn:aff4}). AFF4 URNs are then be made unique by use of 
a unique identifier generated
as per RFC4122\cite{RFC4122}. For example, an AFF4 URN might be
\emph{urn:aff4:bcc02ea5-eeb3-40ce-90cf-7315daf2505e}

In this way we can identify uniquely any evidence without the change
for name collisions. Once a universal identification regime is
created, it is now possible to collect metadata about each object. The
AFF4 model treats metadata as an abstract concept which may exist
independently from the data itself. We term {\em metadata} to be a set
of statements about objects, written in triple notations (Subject,
Attribute, Value), where {\em Subject} is the URN of the object the
statement is made about. Using this system we are able to store
arbitrary attributes about any object in the AFF4 universe. Additionally,
as these statements are universally scoped, they may be stored anywhere.

@@

The AFF4 model is different however. In AFF4 metadata is managed in a location
independant manner 
through a Universal Resolver (perhaps implemented in a database). Relevant information
is found not only in Volumes, but may additionally come from other sources.
This means that in the
above example, the user will query the resolver about the location of
the volume. The resolver returns a URL to the current location of the
volume. The user's library will then open a HTTP Stream instance to
the location returned and the volume may be opened directly over the
intra-web connection.
